### 2023-06-15 manuscript.tex
more bib tweaks. [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/f701f88bde71d6a44507f5904a8e4ac2ad6d69ce.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/f701f88bde71d6a44507f5904a8e4ac2ad6d69ce/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5278088301

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/c01187b0544337b5638fa36c73801550ce98a89a/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/c01187b0544337b5638fa36c73801550ce98a89a}{stain/2022-fdo-paper@c01187b}
on June 15, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/f701f88bde71d6a44507f5904a8e4ac2ad6d69ce/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/f701f88bde71d6a44507f5904a8e4ac2ad6d69ce}{stain/2022-fdo-paper@f701f88}
on June 15, 2023.
